Spatial evolution of solar wind discontinuities in the outer heliosphere

### 2024-11-23 article.qmd
feat: add waiting time figure

::: {#fig-waitingTime}
![](figures/waiting_time_distribution)

Waiting time distribution, along with the fitted Weibull distribution at different radial distances.
:::

>>>>

::: {#fig-waitingTime}
![](figures/fig_wt_dist.pdf)

Waiting time probability density functions $p(\tau)$ for Juno at 1 AU in 2011 (top) and 5 AU in 2016 (bottom). Observed data (black) are fitted with Weibull (blue) and exponential (orange) distributions. In 2011, the Weibull distribution is characterized by parameters $\alpha = 0.99, \theta = 30.29$, and a mean waiting time of 30.41 minutes, while the exponential distribution has a mean of 30.42 minutes. In 2016, the Weibull distribution has parameters $\alpha = 0.65, \theta = 110.50$, and a mean of 150.96 minutes, whereas the exponential distribution has a mean of 165.02 minutes. Vertical dashed lines denote the mean waiting times for each fitted distribution.
:::
